\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Application of artificial intelligence in prosthetics and orthotic rehabiliation}
\author{Submitted by Lingamgunta Saikumar}
\date{19th July 2021}
\begin{document}

\maketitle

\section{Introduction}
Human is the most intelligent creature in the planet for their brain power 
and neural network. The human brain is extremely complex with more 
than 80 billion neurons and trillion of connections . Simulation scales can 
array from molecular and genetic expressions to compartment models of 
subcellular volumes and individual neurons to local networks and system 
models . Deep Neural Network nodes are an over simplification of how 
brain synapses work. Signal transmission in the brain is dominated by 
chemical synapses, which release chemical substances and 
neurotransmitters to convert electrical signals via voltage-gated ion 
channels at the presynaptic cleft into post-synaptic activity. The type of 
neurotransmitter characterizes whether a synapse facilitates signal 
transmission (excitatory role) or prevents it (inhibitory role). Currently, 
there are tenths of known neurotransmitters, whereas new ones 
continuously emerge with varying functional roles. Furthermore, dynamic 
synaptic adaptations, which affect the strength of a synapse, occur in 
response to the frequency and magnitude of the presynaptic signal and 
reflect complex learning/memory functions, (Spike time dependent 
plasticity) . Recently, evidence has found that surrounding cells, such as glia 
cells that are primarily involved in ‘feeding’ the neurons, can also affect 
their function via the release of neurotransmitters .
This new vision of “tripartite synapses” composed of perisynaptic glia in 
addition to pre- and postsynaptic terminals certainly makes this one of the 
most exciting discoveries in current neurobiology . The functional loss due 
to amputation, spinal cord injury, brachial plexus injury or traumatic brain 
injury resulting loss of connection from brain to extremity and those 
residual/weakened extremities are not able to function as of healthy/intact 
limb. These lost structure & functions of extremities were being replaced 
by fitment of prosthetics and orthotic devices or rehabilitation aids. The 
conventional prosthesis which is a mechanical device only provide the basic 
function, similarly Orthosis provides the support to weaken parts not fully 
with out completely mimicking the lost section. The concept of 
biomechatronic is a sub-discipline of mechatronics. It is related to develop 
mechatronics systems which assist or restore to human body gave the 
prosthetics and orthotics concept to a new direction. A biomechatronic 
system has four units: Biosensors, Mechanical Sensors, Controller, and 
Actuator . Biosensors detect intentions of human using biological reactions 
coming from nervous or muscle system. The controller acts as a translator 
among biological and electronic structures, and also monitors the activities 
of the biomechatronic device .
Mechanical sensors measure data about the biomechatronic device and 
relay to the biosensor or controller. The actuator is an artificial muscle 
(robot mechanism) that produces force or movement to aid or replace 
native human body function. The areas of use of biomechatronic are 
orthotics, prosthesis, exoskeleton and rehabilitation robots, and 
neuroprosthesis. Robots are the intelligent devices that easily fulfill the 
requirements of cyclic movements in rehabilitation, better control over 
introduced forces; accurately reproduce required forces in repetitive 
exercises and more precise in different situations.
\end{document}
